---
title: 'ESM 204 Assignment #4'
author: "Laura Ingulsrud & Tess Hooper"
date: "5/28/2019"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}

# Load necessary packages
library(tidyverse)

```

```{r data, include=FALSE}

# Load in data set: marginal cost of carbon abatement for four economic sectors
carbondata <- read_csv("HW4Data.csv")

# Data columns are: 
  # (1) “Abatement”: amount of carbon abatement (tons)
  # (2) “MC_A”: marginal cost of carbon abatement for Sector A ($/ton)
  # (3) “MC_B”: marginal cost of carbon abatement for Sector B ($/ton)
  # (4) “MC_C”: marginal cost of carbon abatement for Sector C ($/ton)
  # (5) “MC_D”: marginal cost of carbon abatement for Sector D ($/ton)

```

##**Technical Appendix**<br>


###1. Estimated Marginal Cost of Abatement for Sectors A, B, C, and D. 
```{r #1, echo = FALSE, include = FALSE}

# 1. Write down a plausible functional form for the marginal cost of abatement for sector A. Use regression analysis to estimate the parameters of that function. Repeating this for sectors B, C, and D will give you a model of the marginal cost of abatement function for each sector.How well do your models fit the data for each sector? You may need to experiment with different functional forms. 

############################# Supply Curve ##############################################

# Do a linear regression through the data for sector A
A_lm <- lm(MC_A ~ Abatement, data = carbondata)
summary(A_lm)
  # intercept = -8.64448
  # Abatement (slope) = 0.57684
  # R^2 = 0.904 (fits really well!)

# Assign coefficients for sector A
A_intercept <- A_lm$coefficients[1]
A_abatement <- A_lm$coefficients[2]

# Create function for sector A (Intercept + Slope(Abatement) * x)
A_supply <- function(x){A_intercept + A_abatement*x}

#####################################################################################
# Do a linear regression through the data for sector B
B_lm <- lm(MC_B ~ Abatement, data = carbondata)
summary(B_lm)
  # intercept = 9.31770
  # Abatement (slope) = 0.19874
  # R^2 = 0.5355 (fits meh)

# Assign coefficients for sector B
B_intercept <- B_lm$coefficients[1]
B_abatement <- B_lm$coefficients[2]

# Create function for sector B
B_supply <- function(x){B_intercept + B_abatement*x}

#####################################################################################

# Do a linear regression through the data for sector C
C_lm <- lm(MC_C ~ Abatement, data = carbondata)
summary(C_lm)
  # intercept = -11.65503
  # Abatement (slope) = 0.78383
  # R^2 = 0.8663 (fits pretty well)

# Assign coefficients for sector C
C_intercept <- C_lm$coefficients[1]
C_abatement <- C_lm$coefficients[2]

# Create function for sector C
C_supply <- function(x){C_intercept + C_abatement*x}

#####################################################################################

# Do a linear regression through the data for sector D
D_lm <- lm(MC_D ~ Abatement, data = carbondata)
summary(D_lm)
  # intercept = 9.68751
  # Abatement (slope) = 0.25993
  # R^2 = 0.5108 (fits meh; the worst of the 4)

# Assign coefficients for sector D
D_intercept <- D_lm$coefficients[1]
D_abatement <- D_lm$coefficients[2]

# Create function for sector D
D_supply <- function(x){D_intercept + D_abatement*x}


# Trying trial graph for D to see if it's linear or quadratic
trial_d <- ggplot(carbondata, aes(x=Abatement, y=MC_D)) +
  geom_point() +
  geom_smooth()

trial_d # Could be quadratic?? Should we do a quadratic function? 

# Keep with linear!

#####################################################################################

# Make stargazer table of coefficients???

#####################################################################################

# Produce a plot of the estimated marginal abatement cost functions in all four sectors (this plot should go in your memo).

plot_allsectors <- ggplot(data.frame(x = c(0,350)), aes(x = x)) + 
    stat_function(fun = A_supply, geom ="line", aes(color = "A")) + 
    stat_function(fun = B_supply, geom ="line", aes(color = "B")) +
    stat_function(fun = C_supply, geom ="line", aes(color = "C")) +
    stat_function(fun = D_supply, geom ="line", aes(color = "D"))+
    labs(x = "Abatement", y = "Price")+
    scale_x_continuous(limits =c(0,350), expand = c(0,0))+
    scale_y_continuous(limits=c(-15,120), expand=c(0,0)) +
    labs(fill = "", color = "Sectors") + # Changes the legend title
    xlab("\n Abatement (tons of Carbon)") + 
    ylab("Abatement Cost \n($/ton of Carbon) \n") +
    ggtitle("Estimated Marginal Abatement Cost for Four Economic Sectors\n") +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"))

plot_allsectors

#####################################################################################

```

$Sector~A~Marginal~Cost~Of~Abatement = `r A_abatement` *Quantity + `r A_intercept`$

$Sector~B~Marginal~Cost~Of~Abatement = `r B_abatement` *Quantity + `r B_intercept`$

$Sector~C~Marginal~Cost~Of~Abatement = `r C_abatement` *Quantity + `r C_intercept`$

$Sector~D~Marginal~Cost~Of~Abatement = `r D_abatement` *Quantity + `r D_intercept`$



<br>


###2. Demand for Carbon Emissions (Sectors A, B, C, and D)

## Sector A:
```{r #2 Sector A, echo = FALSE}

#### 2. Using these models and the current level of carbon emissions, derive each sector’s demand curve for carbon emissions. In other words, how much would each sector be willing to pay for the right to pollute the first unit, second unit, etc? Draw these demand curves on a graph. Which sector is willing to pay the most for the first unit of carbon emissions? 

#########################################################################

#### SECTOR A WILLINGNESS TO PAY

# Current emissions are 180 - use quantities from 0 to 180 by 10

quantity_a <- seq(0,180,by=10)


# Write function for demand curve for Sector A
demand_A <- function(q){
  (A_abatement*(180-q)) + A_intercept
}

demand_A


# Derive demand curve using the values above
d_curve_A <- demand_A(quantity_a)



# # Graph the demand curve
# curve(demand_A, from=0, to=180, xlab = "Carbon Emissions (tons)", ylab = "$/Ton")


### Plug in 0 to the function to calculate how much Sector A is willing to pay to emit the first unit of Carbon

WTP_A <- (A_abatement*(180-0) + A_intercept)
# 95.18706

# Sector A is willing to pay $95.19 for the first ton of emissions 


```

$Price~of~Emissions = `r A_abatement`*(180-Quantity) + `r A_intercept`$  
 - Willingness to Pay for First Unit = \$95.19 
 
 <br>
 
## Sector B:
```{r #2 Sector B, echo = FALSE}

### SECTOR B WILLINGNESS TO PAY


# Current emissions are 200 - use quantities from 0 to 200 by 10

quantity_b <- seq(0,200,by=10)


# Write function for demand curve for Sector A
demand_B <- function(q){
  (B_abatement*(200-q)) + B_intercept
}

demand_B


# Derive demand curve using the values above
d_curve_B <- demand_B(quantity_b)



# # Graph the demand curve
# curve(demand_B, from=0, to=200, xlab = "Carbon Emissions (tons)", ylab = "$/Ton")


### Plug in 0 to the function to calculate how much Sector A is willing to pay to emit the first unit of Carbon

WTP_B <- (B_abatement*(200-0) + B_intercept)
# 49.06656 

# Sector B is willing to pay $49.07 for the first ton of emissions 

```
 
$Price~of~Emissions = `r B_abatement`*(200-Quantity) + `r B_intercept`$  
 - Willingness to Pay for First Unit = \$49.07 

<br>


## Sector C:
```{r, #2 Sector C, echo = FALSE}

### SECTOR C WILLINGNESS TO PAY


# Current emissions are 220 - use quantities from 0 to 220 by 10

quantity_c <- seq(0,220,by=10)


# Write function for demand curve for Sector A
demand_C <- function(q){
  (C_abatement*(220-q)) + C_intercept
}

demand_C


# Derive demand curve using the values above
d_curve_C <- demand_C(quantity_c)



# # Graph the demand curve
# curve(demand_C, from=0, to=220, xlab = "Carbon Emissions (tons)", ylab = "$/Ton")


### Plug in 0 to the function to calculate how much Sector A is willing to pay to emit the first unit of Carbon

WTP_C <- (C_abatement*(220-0) + C_intercept)
# 160.7868

# Sector C is willing to pay $161.79 for the first ton of emissions

```

$Price~of~Emissions = `r C_abatement`*(220-Quantity) + `r C_intercept`$  
 - Willingness to Pay for First Unit = \$161.79 
 
 <br>
 
 ## Sector D:
```{r #2 Sector D, echo = FALSE}


### SECTOR D WILLINGNESS TO PAY

# Current emissions are 300 - use quantities from 0 to 300 by 10

quantity_d <- seq(0,300,by=10)


# Write function for demand curve for Sector A
demand_D <- function(q){
  (D_abatement*(300-q)) + D_intercept
}

demand_D


# Derive demand curve using the values above
d_curve_D <- demand_D(quantity_d)



# # Graph the demand curve
# curve(demand_D, from=0, to=300, xlab = "Carbon Emissions (tons)", ylab = "$/Ton")


### Plug in 0 to the function to calculate how much Sector A is willing to pay to emit the first unit of Carbon

WTP_D <- (D_abatement*(300-0) + D_intercept)
# 87.66577
# Sector D is willing to pay 87.67 for the first ton of emissions

### WTP will be very different if we use quadratic function ****



```
 
$Price~of~Emissions = `r D_abatement`*(300-Quantity) + `r D_intercept`$  
 - Willingness to Pay for First Unit = \$87.67 
 
 <br>

##Plot
```{r #2 Plot of Demand Curves, include=FALSE}

# Produce a plot of the estimated marginal abatement cost functions in all four sectors (this plot should go in your memo).

plot_demand <- ggplot(data.frame(x = c(0,350))) + 
    stat_function(fun = demand_A, aes(color = "A")) + 
    stat_function(fun = demand_B, aes(color = "B")) +
    stat_function(fun = demand_C, aes(color = "C")) +
    stat_function(fun = demand_D, aes(color = "D"))+
    labs(x = "Emissions", y = "Price")+
    scale_x_continuous(limits =c(0,300), expand = c(0,0))+
    scale_y_continuous(limits=c(0,170), expand=c(0,0)) +
    labs(fill = "", color = "Sectors") + # Changes the legend title
    xlab("\n Emissions (tons of Carbon)") + 
    ylab("Emission Cost \n($/ton of Carbon) \n") +
    ggtitle("Estimated Marginal Emission Benefit for Four Economic Sectors\n") +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"))

plot_demand

```

 
 <br>

###3a. Cap on Carbon Emissions per Sector for Country X (Sectors A, B, C)
```{r #3a}

### 3. Now focus on country X (which contains sectors A, B, and C). Assume there are no “co-benefits” from carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement). Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half. For each of the policy options listed below, derive: (1) the total cost of meeting the target in country X, (2) the cost (or benefit) to each sector, and (3) the tax revenue generated. 

# A. Cap on carbon. Each sector (A, B, and C) must cut its carbon emissions by 100 tons (thus reducing total emissions from 600 down to 300). 

################################### Sector A ################################### 

# Create abatement curve function
abate_A <- function(q){
  (A_abatement*q) + A_intercept
}
# q = quantity abated

# Since each sector must cut its carbon emissions by 100 tons, plug in 100 for q
cap_A <- abate_A(100) 
# 49.03971  # marginal cost (which is the derivative of the total; will need to integrate to find the total)

# Integrate to find the area under the marginal cost curve
MCarea_A <- integrate(abate_A, lower = 0, upper = 100)$value

################################### Sector B ################################### 

# Create abatement curve function
abate_B <- function(q){
  (B_abatement*q) + B_intercept
}

# Since each sector must cut its carbon emissions by 100 tons, plug in 100 for q
cap_B <- abate_B(100) 
# 49.03971  # marginal cost (which is the derivative of the total; will need to integrate to find the total)

# Integrate to find the area under the marginal cost curve
MCarea_B <- integrate(abate_B, lower = 0, upper = 100)$value

################################### Sector C ################################### 

# Create abatement curve function
abate_C <- function(q){
  (C_abatement*q) + C_intercept
}

# Since each sector must cut its carbon emissions by 100 tons, plug in 100 for q
cap_C <- abate_C(100) 
# 49.03971  # marginal cost (which is the derivative of the total; will need to integrate to find the total)

# Integrate to find the area under the marginal cost curve
MCarea_C <- integrate(abate_C, lower = 0, upper = 100)$value

################################### TOTAL ################################### 

# Add all the integrated areas together to get the total cost of each sector abating 100 tons
MCarea_total <- MCarea_A + MCarea_B + MCarea_C
# 6698.883

```
1. Total Cost of Cap on Carbon to Country X
$Total~Cost~to~Country~X = \$`r round(MCarea_total, digits=2)`$   

2. Cost to Each Sector in Country X  
$Cost~to~Sector~A = \$`r round(MCarea_A, digits=2)`$    

$Cost~to~Sector~B = \$`r round(MCarea_B, digits=2)`$    

$Cost~to~Sector~C = \$`r round(MCarea_A, digits=2)`$    

3. Tax Revenue Generated for Country X 

A carbon cap just limits the amount of carbon emitted, it does not tax emissions; therefore no tax revenue is generated.
<br>

###3b. Tax on Carbon that will Accomplish Desired Reduction in Country X
```{r #3b}
### 3. Now focus on country X (which contains sectors A, B, and C). Assume there are no “co-benefits” from carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement). Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half. For each of the policy options listed below, derive: (1) the total cost of meeting the target in country X, (2) the cost (or benefit) to each sector, and (3) the tax revenue generated. 

# B. Tax on carbon. To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction. 

################################### Sector A ################################### 

# Put equation for sector A in terms of q
A_intercept_q <- (-A_intercept/A_abatement)
A_slope_q <- (1/A_abatement)
A_abate_q <- function(p){A_intercept_q + (A_slope_q*p)}

################################### Sector B ################################### 

# Put equation for sector B in terms of q
B_intercept_q <- (-B_intercept/B_abatement)
B_slope_q <- (1/B_abatement)
B_abate_q <- function(p){B_intercept_q + (B_slope_q*p)}

################################### Sector C ################################### 

# Put equation for sector C in terms of q
C_intercept_q <- (-C_intercept/C_abatement)
C_slope_q <- (1/C_abatement)
C_abate_q <- function(p){C_intercept_q + (C_slope_q*p)}

################################### Aggregate Abatement Curve ############################# 

# Find the aggregate intercept
Agg_intercept_q <- sum(A_intercept_q,B_intercept_q,C_intercept_q)

# Find the aggregate intercept
Agg_slope_q <- sum(A_slope_q, B_slope_q, C_slope_q)

# Put equations back in terms of p
Agg_intercept_p <- (-Agg_intercept_q/Agg_slope_q)
Agg_slope_p <- (1/Agg_slope_q)

# Create aggregate demand curve in terms of p
Agg_demandcurve_p <- function(x){Agg_intercept_p + Agg_slope_p*x}

# Find the optimal tax with reduction of 300 tons of carbon
Tax_300 <- Agg_demandcurve_p(300)
# Optimal tax = $39.42658

# # Add up the equations in terms of q for A, B, and C to get aggregate 
# Agg_abate_q <- function(p){A_abate_q + B_abate_q + C_abate_q}

##################### Find quantities under optimal tax #####################

# Sector A emissions (q) under optimal tax
A_tax_emissions <- A_abate_q(Tax_300)
A_tax_emissions
# 83.33489

# Sector B emissions (q) under optimal tax
B_tax_emissions <- B_abate_q(Tax_300)
B_tax_emissions
# 151.4956

# Sector C emissions (q) under optimal tax
C_tax_emissions <- C_abate_q(Tax_300)
C_tax_emissions
# 65.16953

##################### Find cost under optimal tax #####################

# Sector A cost of tax
A_tax_cost <- integrate(A_supply, 0, A_tax_emissions)$value + (180 - A_tax_emissions)*Tax_300
A_tax_cost
# $5093.786

# Sector B cost of tax
B_tax_cost <- integrate(B_supply, 0, B_tax_emissions)$value + (200 - B_tax_emissions)*Tax_300
B_tax_cost
# $5604.635 

# Sector C cost of tax
C_tax_cost <- integrate(C_supply, 0, C_tax_emissions)$value + (220 - C_tax_emissions)*Tax_300
C_tax_cost
# $7009.365

# Total country X cost of tax
Total_tax_cost <- A_tax_cost + B_tax_cost + C_tax_cost
Total_tax_cost
# $17707.79

Total_tax_rev <- 300*Tax_300
Total_tax_rev
# $11827.97

```
1. Total Cost of Tax on Carbon to Country X <br>
$Total~Cost~to~Country~X = \$`r round(Total_tax_cost, digits=2)`$   

2. Cost to Each Sector in Country X <br>
$Cost~to~Sector~A = \$`r round(A_tax_cost, digits=2)`$    

$Cost~to~Sector~B = \$`r round(B_tax_cost, digits=2)`$    

$Cost~to~Sector~C = \$`r round(C_tax_cost, digits=2)`$    

3. Tax Revenue Generated for Country X <br>
$Total~Tax~Revenue~for~Country~X = \$`r round(Total_tax_rev, digits=2)`$
<br>

###3c. Cap and Trade Outcomes per Sector in Country X (Sectors A, B, C)
```{r #3c}
### 3. Now focus on country X (which contains sectors A, B, and C). Assume there are no “co-benefits” from carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement). Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half. For each of the policy options listed below, derive: (1) the total cost of meeting the target in country X, (2) the cost (or benefit) to each sector, and (3) the tax revenue generated. 

# C. Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissions minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three sectors are allowed to trade with each other. You will need to derive the outcome of that trading. 

################################### Sector A ################################### 

# How much sector A will buy
A_cat <- (180-A_tax_emissions-80)
A_cat
# 16.66511  

# Cost of sector A abating 83.3 units and buying 16.67 carbon credits from sector B
A_cat_cost <- integrate(A_supply, lower = 0, upper = A_tax_emissions)$value + (16.66511*Tax_300)
A_cat_cost
# $1939.66

################################### Sector B ################################### 

# How much sector B will sell
B_cat <- (200-B_tax_emissions-100)
B_cat
# -51.49558 

# Cost of sector B abating 151.5 units and selling 51.5 carbon credits to sectors A and C
B_cat_cost <- integrate(B_supply, lower = 0, upper = B_tax_emissions)$value - (51.49558*Tax_300)
B_cat_cost
# $1661.977

################################### Sector C ################################### 

# How much sector C will buy
C_cat <- (220-C_tax_emissions-120)
C_cat
# 34.83047

# Cost of sector C abating 65.2 units and buying 34.8 carbon credits from sector B
C_cat_cost <- integrate(C_supply, lower = 0, upper = C_tax_emissions)$value + (34.83047*Tax_300)
C_cat_cost
# $2278.176

################################### TOTAL ################################### 

# Total cost of cap and trade program
Total_cat_cost <- A_cat_cost + B_cat_cost + C_cat_cost
Total_cat_cost
# $5879.812

```
1. Total Cost of Cap and Trade to Country X
$Total~Cost~to~Country~X = \$`r round(Total_cat_cost, digits=2)`$   

2. Cost to Each Sector in Country X  
$Cost~to~Sector~A = \$`r round(A_cat_cost, digits=2)`$    

$Cost~to~Sector~B = \$`r round(B_cat_cost, digits=2)`$    

$Cost~to~Sector~C = \$`r round(C_cat_cost, digits=2)`$    

3. Tax Revenue Generated for Country X 

A cap and trade program limits the total amount of carbon emitted but allows trading between sectors. It does not tax emissions, so no tax revenue is generated.
<br>

###4. Incentivizing Carbon Market for Country Y
```{r #4}

# Again, without any co-benefits, suppose that country Y (which only has one carbon-emitting sector, D) has no obligation to reduce its emissions. Country X asks country Y to enter the country X carbon market. Doing so would require country Y to put a cap on carbon emissions at its current level of emissions (300 tons), but would then allow country Y to sell carbon offsets to sectors A, B, or C. Are there any incentives for country Y to enter country X’s carbon market and to thus place a voluntary cap on its emissions? Are there any incentives for country X to try to attract country Y into its market? 

# Find price for sector D supply curve at quantity 300
D_price_300 <- D_supply(300)
D_price_300
# $87.66577

################################### Sector D ################################### 

# Put equation for sector D in terms of q
D_intercept_q <- (-D_intercept/D_abatement)
D_slope_q <- (1/D_abatement)
D_abate_q <- function(p){D_intercept_q + (D_slope_q*p)}

########################### Aggregate Demand Curve ############################ 

# Find the aggregate intercept
D_Agg_intercept_q <- sum(A_intercept_q, B_intercept_q, C_intercept_q, D_intercept_q)

# Find the aggregate intercept
D_Agg_slope_q <- sum(A_slope_q, B_slope_q, C_slope_q, D_slope_q)

# Put equations back in terms of p
D_Agg_intercept_p <- (-D_Agg_intercept_q/D_Agg_slope_q)
D_Agg_slope_p <- (1/D_Agg_slope_q)

# Create aggregate demand curve in terms of p
D_Agg_demandcurve_p <- function(x){D_Agg_intercept_p + D_Agg_slope_p*x}

# Find the optimal tax with reduction of 300 tons of carbon
D_Tax_300 <- D_Agg_demandcurve_p(300)
D_Tax_300
# Optimal tax = $29.80249

# Quantity of emissions sectors abate at the new optimal tax ($29.80)
A_emissions_tax_new <- (D_Tax_300 - A_intercept)/A_abatement
A_emissions_tax_new
# 66.65079 

B_emissions_tax_new <- (D_Tax_300 - B_intercept)/B_abatement
B_emissions_tax_new
# 103.0711

C_emissions_tax_new <- (D_Tax_300 - C_intercept)/C_abatement
C_emissions_tax_new
# 52.89119

D_emissions_tax_new <- (D_Tax_300 - D_intercept)/D_abatement
D_emissions_tax_new
# 77.3869

# Cost of sectors abating at the new optimal tax:
# Sector A needs to cut by 100, abates 66.65079, so buys the following:
A_cost_tax_new <- integrate(A_supply, 0, A_emissions_tax_new)$value + ((100-66.65079)*D_Tax_300)
A_cost_tax_new
# $1698.989
  
# Sector B needs to cut by 100, abates 103.0711, so buys the following:
B_cost_tax_new <- integrate(B_supply, 0, B_emissions_tax_new)$value + ((100-103.0711)*D_Tax_300)
B_cost_tax_new
# $1924.554

# Sector C needs to cut by 100, abates 52.89119, so buys the following:
C_cost_tax_new <- integrate(C_supply, 0, C_emissions_tax_new)$value + ((100-52.89119)*D_Tax_300)
C_cost_tax_new
# $1883.88

# Sector D needs to cut by 0 (sells all), abates 77.3869, so buys the following:
D_cost_tax_new <- integrate(D_supply, 0, D_emissions_tax_new)$value - (77.3869*D_Tax_300)
D_cost_tax_new
# $-778.3182

# Cost of country X and Y
Total_cost_tax_new <- A_cost_tax_new + B_cost_tax_new + C_cost_tax_new + D_cost_tax_new
Total_cost_tax_new
# $4729.105

# Cost of Country X ONLY 
country_X_cost <- A_cost_tax_new + B_cost_tax_new + C_cost_tax_new 
country_X_cost
# $5507.424

```
After Country Y enters Country X's carbon market, Sector D is added to the aggregate demand curve of Sectors A, B, and C. The new optimal price of emitting/marginal cost of abatement ($/ton) with the addition of Sector D is \$`r round(D_Tax_300, digits=2)`. This is less than the marginal cost of abatement for Country X on its own (\$`r round(Tax_300, digits=2)`). After finding the new optimal emissions quantity for each sector based on this new marginal cost of abatement, and the new cost of abatement for each sector, the new total cost of abatement of 300 tons for Country X and Y combined is \$`r round(Total_cost_tax_new, digits=2)`.

The cost of a cap and trade program to Country X (without Country Y) is \$`r round(country_X_cost, digits=2)`. The cost of a cap and trade program to Country Y is \$`r round(D_cost_tax_new, digits=2)`. Since Country Y has a negative cost of entering the cap and trade program, they are incentivized to join Country X's carbon market, since Country X's sectors will want to buy carbon credits from Country Y. Country X also has an incentive to attract Country Y into its market, because the total cost of their carbon market program decreases once Country Y joins (from \$`r round(country_X_cost, digits=2)` to \$`r round(Total_cost_tax_new, digits=2)`).
<br>

###5a. Country X Only Carbon Market: Amount of Expected Local Air Pollution in Country X and Country Y 
```{r #5a}

### Now assume that every ton of carbon emissions creates 1 ton of local air pollution. Local air pollution causes economic damages (health, environmental, etc.), but only in the country in which it is emitted. Assume there are no local air pollution regulations in either country X or country Y. 

# A. In a carbon cap and trade market that only covers sectors in country X, how much local air pollution would you expect in country X? In country Y? 


X_pollution <- 600 - (A_tax_emissions + B_tax_emissions + C_tax_emissions)
X_pollution
# 300 tons

Y_pollution <- 300
# 300 tons


```
The previous scenarios have not considered any local air pollutant emissions caused by emitting carbon. There are local air pollutants associated with the emission of carbon, which can have economic damages (health and environmental consequences) in the country in which it is emitted. In a carbon cap and trade market that only covers sectors in Country X, we would expect `r round(X_pollution, digits=2)` tons of local air pollutants. In Country Y, we would expect `r round(Y_pollution, digits=2)` tons of local air pollutants. 

###5b. Country X and Y Carbon Market: Amount of Expected Local Air Pollution in Country X and Country Y 
```{r #5b}


# B. If country Y enters the carbon market for country X (as in question 4 above), how much local pollution will there be in country X and country Y? 

  
X_pollution_afterY <- 600 - (A_emissions_tax_new + B_emissions_tax_new + C_emissions_tax_new)
X_pollution_afterY
# 377.3869 tons

Y_pollution_afterY <- 300 - D_emissions_tax_new
Y_pollution_afterY
# 222.6131 tons

```
In a carbon cap and trade market that covers all sectors in both Country X and Country Y, we would expect `r round(X_pollution_afterY, digits=2)` tons of local air pollutants. In Country Y, we would expect `r round(Y_pollution_afterY, digits=2)` tons of local air pollutants. 


###5c. Desirability of Allowing International Trade of Carbon Emission Credits
```{r #5c}

# C. What advice can you give country X and country Y about the desirability of allowing international trade of carbon emissions credits?

```
By participating in an international cap and trade program, net emissions/air pollution across the two countries stay the same, but local air pollution will be reduced in Country Y, and local air pollution will increase in Country X, because Sectors A and C will buy carbon credits from Sector D. While an international cap and trade program is economically beneficial to both countries, the environmental impacts and distributional effects are not beneficial to Country X.
