---
title: 'ESM 204 Assignment #4'
author: "Laura Ingulsrud & Tess Hooper"
date: "5/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}

# Load necessary packages
library(tidyverse)

```

```{r data, include=FALSE}

# Load in data set: marginal cost of carbon abatement for four economic sectors
carbondata <- read_csv("HW4Data.csv")

# Data columns are: 
  # (1) “Abatement”: amount of carbon abatement (tons)
  # (2) “MC_A”: marginal cost of carbon abatement for Sector A ($/ton)
  # (3) “MC_B”: marginal cost of carbon abatement for Sector B ($/ton)
  # (4) “MC_C”: marginal cost of carbon abatement for Sector C ($/ton)
  # (5) “MC_D”: marginal cost of carbon abatement for Sector D ($/ton)

```

##**Technical Appendix**<br>


###1. Estimated Marginal Cost Functions for Sectors A, B, C, and D. 
```{r #1}

# 1. Write down a plausible functional form for the marginal cost of abatement for sector A. Use regression analysis to estimate the parameters of that function. Repeating this for sectors B, C, and D will give you a model of the marginal cost of abatement function for each sector.How well do your models fit the data for each sector? You may need to experiment with different functional forms. 

#####################################################################################

# Do a linear regression through the data for sector A
A_lm <- lm(MC_A ~ Abatement, data = carbondata)
summary(A_lm)
  # intercept = -8.64448
  # Abatement (slope) = 0.57684
  # R^2 = 0.904 (fits really well!)

# Assign coefficients for sector A
A_intercept <- A_lm$coefficients[1]
A_abatement <- A_lm$coefficients[2]

# Create function for sector A (Intercept + Slope(Abatement) * x)
A <- function(x){A_intercept + A_abatement*x}

#####################################################################################
# Do a linear regression through the data for sector B
B_lm <- lm(MC_B ~ Abatement, data = carbondata)
summary(B_lm)
  # intercept = 9.31770
  # Abatement (slope) = 0.19874
  # R^2 = 0.5355 (fits meh)

# Assign coefficients for sector B
B_intercept <- B_lm$coefficients[1]
B_abatement <- B_lm$coefficients[2]

# Create function for sector B
B <- function(x){B_intercept + B_abatement*x}

#####################################################################################

# Do a linear regression through the data for sector C
C_lm <- lm(MC_C ~ Abatement, data = carbondata)
summary(C_lm)
  # intercept = -11.65503
  # Abatement (slope) = 0.78383
  # R^2 = 0.8663 (fits pretty well)

# Assign coefficients for sector C
C_intercept <- C_lm$coefficients[1]
C_abatement <- C_lm$coefficients[2]

# Create function for sector C
C <- function(x){C_intercept + C_abatement*x}

#####################################################################################

# Do a linear regression through the data for sector D
D_lm <- lm(MC_D ~ Abatement, data = carbondata)
summary(D_lm)
  # intercept = 9.68751
  # Abatement (slope) = 0.25993
  # R^2 = 0.5108 (fits meh; the worst of the 4)

# Assign coefficients for sector D
D_intercept <- D_lm$coefficients[1]
D_abatement <- D_lm$coefficients[2]

# Create function for sector D
D <- function(x){D_intercept + D_abatement*x}


# Trying trial graph for D to see if it's linear or quadratic
trial_d <- ggplot(carbondata, aes(x=Abatement, y=MC_D)) +
  geom_point() +
  geom_smooth()

trial_d # Could be quadratic?? Should we do a quadratic function? 

# Keep with linear!


#####################################################################################

# Produce a plot of the estimated marginal abatement cost functions in all four sectors (this plot should go in your memo).

plot_allsectors <- ggplot(data.frame(x = c(0,350)), aes(x = x)) + 
    stat_function(fun = A, geom ="line", aes(color = "A")) + 
    stat_function(fun = B, geom ="line", aes(color = "B")) +
    stat_function(fun = C, geom ="line", aes(color = "C")) +
    stat_function(fun = D, geom ="line", aes(color = "D"))+
    labs(x = "Abatement", y = "Price")+
    scale_x_continuous(limits =c(0,350), expand = c(0,0))+
    scale_y_continuous(limits=c(-15,120), expand=c(0,0)) +
    labs(fill = "", color = "Sectors") + # Changes the legend title
    xlab("\n Abatement (tons of Carbon)") + 
    ylab("Abatement Cost \n($/ton of Carbon) \n") +
    ggtitle("Estimated Marginal Abatement Cost for Four Economic Sectors\n") +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"))

plot_allsectors

#####################################################################################

```

$Marginal~Cost~Of~Abatement~Sector~A = `r A_abatement` *Quantity + `r A_intercept`$

$Marginal~Cost~Of~Abatement~Sector~B = `r B_abatement` *Quantity + `r B_intercept`$

$Marginal~Cost~Of~Abatement~Sector~C = `r C_abatement` *Quantity + `r C_intercept`$

$Marginal~Cost~Of~Abatement~Sector~D = `r D_abatement` *Quantity + `r D_intercept`$



<br>


###2. Demand Curves for Carbon Emissions (Sectors A, B, C, and D)

## Sector A:
```{r #2 Sector A, echo = FALSE}

#### Using these models and the current level of carbon emissions, derive each sector’s demand curve for carbon emissions. In other words, how much would each sector be willing to pay for the right to pollute the first unit, second unit, etc? Draw these demand curves on a graph. Which sector is willing to pay the most for the first unit of carbon emissions? 

#########################################################################

#### SECTOR A WILLINGNESS TO PAY

# Current emissions are 180 - use quantities from 0 to 180 by 10

quantity_a <- seq(0,180,by=10)


# Write function for demand curve for Sector A
demand_A <- function(q){
  (A_abatement*(180-q)) + A_intercept
}

demand_A


# Derive demand curve using the values above
d_curve_A <- demand_A(quantity_a)



# Graph the demand curve
curve(demand_A, from=0, to=180, xlab = "Carbon Emissions (tons)", ylab = "$/Ton")


### Plug in 0 to the function to calculate how much Sector A is willing to pay to emit the first unit of Carbon

WTP_A <- (A_abatement*(180-0) + A_intercept)

# Sector A is willing to pay 95.20 for the first ton of emissions 


```

$Price~of~Emissions = `r A_abatement`*(180-Quantity) + `r A_intercept`$  
 - Willingness to Pay for First Unit = \$95.20 
 
 <br>
 
## Sector B:
```{r Sector B, echo = FALSE}

### SECTOR B WILLINGNESS TO PAY


# Current emissions are 200 - use quantities from 0 to 200 by 10

quantity_b <- seq(0,200,by=10)


# Write function for demand curve for Sector A
demand_B <- function(q){
  (B_abatement*(200-q)) + B_intercept
}

demand_B


# Derive demand curve using the values above
d_curve_B <- demand_B(quantity_b)



# Graph the demand curve
curve(demand_B, from=0, to=200, xlab = "Carbon Emissions (tons)", ylab = "$/Ton")


### Plug in 0 to the function to calculate how much Sector A is willing to pay to emit the first unit of Carbon

WTP_B <- (B_abatement*(200-0) + B_intercept)

# Sector B is willing to pay 49.10 for the first ton of emissions 

```
 
$Price~of~Emissions = `r B_abatement`*(200-Quantity) + `r B_intercept`$  
 - Willingness to Pay for First Unit = \$49.10 

<br>


## Sector C:
```{r, Sector C, echo = FALSE}

### SECTOR C WILLINGNESS TO PAY


# Current emissions are 220 - use quantities from 0 to 220 by 10

quantity_c <- seq(0,220,by=10)


# Write function for demand curve for Sector A
demand_C <- function(q){
  (C_abatement*(220-q)) + C_intercept
}

demand_C


# Derive demand curve using the values above
d_curve_C <- demand_C(quantity_c)



# Graph the demand curve
curve(demand_C, from=0, to=220, xlab = "Carbon Emissions (tons)", ylab = "$/Ton")


### Plug in 0 to the function to calculate how much Sector A is willing to pay to emit the first unit of Carbon

WTP_C <- (C_abatement*(220-0) + C_intercept)

# Sector C is willing to pay 161.00 for the first ton of emissions   **** CHECK VALUES --- ROUNDING IS OFF?

```

$Price~of~Emissions = `r C_abatement`*(220-Quantity) + `r C_intercept`$  
 - Willingness to Pay for First Unit = \$161.10 
 
 <br>
 
 ## Sector D:
```{r Sector D, echo = FALSE}


### SECTOR D WILLINGNESS TO PAY

# Current emissions are 300 - use quantities from 0 to 300 by 10

quantity_d <- seq(0,300,by=10)


# Write function for demand curve for Sector A
demand_D <- function(q){
  (D_abatement*(300-q)) + D_intercept
}

demand_D


# Derive demand curve using the values above
d_curve_D <- demand_D(quantity_d)



# Graph the demand curve
curve(demand_D, from=0, to=300, xlab = "Carbon Emissions (tons)", ylab = "$/Ton")


### Plug in 0 to the function to calculate how much Sector A is willing to pay to emit the first unit of Carbon

WTP_D <- (D_abatement*(300-0) + D_intercept)

# Sector D is willing to pay 87.70 for the first ton of emissions   **** CHECK VALUES --- ROUNDING IS OFF? 

### WTP will be very different if we use quadratic function ****



```
 
$Price~of~Emissions = `r D_abatement`*(300-Quantity) + `r D_intercept`$  
 - Willingness to Pay for First Unit = \$87.70 
 
 <br>
 <br>
 

###3a. Cap on Carbon Emissions per Sector (A, B, C only)
```{r #3a}

### Now focus on country X (which contains sectors A, B, and C). Assume there are no “co-benefits” from carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement). Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half. For each of the policy options listed below, derive: (1) the total cost of meeting the target in country X, (2) the cost (or benefit) to each sector, and (3) the tax revenue generated. 

# A. Cap on carbon. Each sector (A, B, and C) must cut its carbon emissions by 100 tons (thus reducing total emissions from 600 down to 300). 


```

###3b. Tax on Carbon that will Accomplish Desired Reduction in Country X
```{r #3b}

# B. Tax on carbon. To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction. 

```

###3c. Cap and Trade Outcomes per Sector (A, B, C only)
```{r #3c}


# C. Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissions minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three sectors are allowed to trade with each other. You will need to derive the outcome of that trading. 




```

###4. Incentivizing Carbon Market for Country Y
```{r #4}

# Again, without any co-benefits, suppose that country Y (which only has one carbon-emitting sector, D) has no obligation to reduce its emissions. Country X asks country Y to enter the country X carbon market. Doing so would require country Y to put a cap on carbon emissions at its current level of emissions (300 tons), but would then allow country Y to sell carbon offsets to sectors A, B, or C. Are there any incentives for country Y to enter country X’s carbon market and to thus place a voluntary cap on its emissions? Are there any incentives for country X to try to attract country Y into its market? 



```

###5a. Country X Only Carbon Market: Amount of Expected Local Air Pollution in Country X and Country Y 
```{r #5a}

### Now assume that every ton of carbon emissions creates 1 ton of local air pollution. Local air pollution causes economic damages (health, environmental, etc.), but only in the country in which it is emitted. Assume there are no local air pollution regulations in either country X or country Y. 

# A. In a carbon cap and trade market that only covers sectors in country X, how much local air pollution would you expect in country X? In country Y? 




```

###5b. Country X and Y Carbon Market: Amount of Expected Local Air Pollution in Country X and Country Y 
```{r #5b}


# B. If country Y enters the carbon market for country X (as in question 4 above), how much local pollution will there be in country X and country Y? 

  



```

###5c. Desirability of Allowing International Trade of Carbon Emission Credits
```{r #5c}

# C. What advice can you give country X and country Y about the desirability of allowing international trade of carbon emissions credits?



```
